Open archaeology, open source?

### 2023-10-11 analysis/openarchaeo_collaboration.qmd
Add affiliation URLs
Because why not

---
title: Open archaeology, open source?
subtitle: Collaborative practices in an emerging community of archaeological software engineers
author:
  - name: Zack Batist
    url: https://zackbatist.info
    affiliation: Faculty of Information, University of Toronto
    orcid: 0000-0003-0435-508X 
  - name: Joe Roe
    url: https://joeroe.io
    affiliation: Institute of Archaeological Sciences, University of Bern
    orcid: 0000-0002-1011-1244
date: "`r Sys.Date()`"
abstract: |
  Surveying the first quarter-century of computer applications in archaeology, Scollar [-@scollar1999] lamented that the field relied almost exclusively on "hand-me-down" tools repurposed from other disciplines.  25 years later, this is no longer the case: computational archaeologists often find themselves practicing the dual roles of data analyst and research software engineer [@baxter2012], developing and applying new tools that are tailored specifically to archaeological problems and archaeological methods. Though this trend can be traced to the very earliest days of the field [@cowgill1967], its most recent manifestation is distinguished by its apparently embrace of practices from free and open source software (FOSS). Most prominently, since around 2015, there has been a rapid uptake of workflow tools designed for open source development communities, such as the version control system `git` and associated online source code management platforms (e.g. GitHub, GitLab). These tools facilitate collaboration among developers and users of FOSS software using patterns that can diverge quite radically from conventional scholarly norms [@tennant2020].

>>>>

---
title: Open archaeology, open source?
subtitle: Collaborative practices in an emerging community of archaeological software engineers
author:
  - name: Zack Batist
    url: https://zackbatist.info
    affiliation: Faculty of Information, University of Toronto
    affiliation-url: https://ischool.utoronto.ca/
    orcid: 0000-0003-0435-508X 
  - name: Joe Roe
    url: https://joeroe.io
    affiliation: Institute of Archaeological Sciences, University of Bern
    affiliation-url: https://www.iaw.unibe.ch/
    orcid: 0000-0002-1011-1244
date: "`r Sys.Date()`"
abstract: |
  Surveying the first quarter-century of computer applications in archaeology, Scollar [-@scollar1999] lamented that the field relied almost exclusively on "hand-me-down" tools repurposed from other disciplines.  25 years later, this is no longer the case: computational archaeologists often find themselves practicing the dual roles of data analyst and research software engineer [@baxter2012], developing and applying new tools that are tailored specifically to archaeological problems and archaeological methods. Though this trend can be traced to the very earliest days of the field [@cowgill1967], its most recent manifestation is distinguished by its apparently embrace of practices from free and open source software (FOSS). Most prominently, since around 2015, there has been a rapid uptake of workflow tools designed for open source development communities, such as the version control system `git` and associated online source code management platforms (e.g. GitHub, GitLab). These tools facilitate collaboration among developers and users of FOSS software using patterns that can diverge quite radically from conventional scholarly norms [@tennant2020].
